---
title: "Marketing Channel Performance Dashboard"
author: "Zhongyi (Yee) Sun"
format:
  dashboard:
    logo: productfolio-logo-wht-1.png
    reader-mode: false
    page-layout: full
    orientation: rows
    sidebar:
      collapse: true
    navbar:
      background: secondary
execute:
  freeze: auto
---

```{r setup, include=FALSE}

library(tidyverse)
library(readr)
library(kableExtra)

# Load data
raw <- read_csv("All_channels.csv")
# Process data
processed <- raw %>%
  rename(
    channel_group = `Primary channel group (Default Channel Group)`,
    key_events = `Key events`,
    ads_cpc = `Ads cost per click`,
    roas = `Return on ad spend`
  ) %>%
  group_by(channel_group) %>%
  summarise(
    total_events = sum(key_events, na.rm = TRUE),
    avg_cpc = mean(ads_cpc, na.rm = TRUE),
    avg_roas = mean(roas, na.rm = TRUE)
  ) %>%
  ungroup()
```

::: {card="📊 Overview"}
This dashboard provides a comprehensive view of **marketing channel performance** using the latest campaign data. Explore key metrics such as total key events, cost-per-click efficiency, and return on ad spend (ROAS).
:::

##  {.sidebar}

::: {value-box}
**Total Events**\
`r sum(processed$total_events)`
:::

::: {value-box}
**Avg. CPC**\
`r round(mean(processed$avg_cpc, na.rm = TRUE), 2)`
:::

::: {value-box}
**Avg. ROAS**\
`r round(mean(processed$avg_roas, na.rm = TRUE), 2)`
:::

## 

------------------------------------------------------------------------

::: {card="🔹 Scatter: Events vs ROAS"}
```{r fig.width=8, fig.height=4}
#| title: Overview
ggplot(processed, aes(x = total_events, y = avg_roas, color = channel_group)) +
  geom_point(size = 4) +
  geom_smooth(method = "lm", se = FALSE, color = "#333333") +
  theme_minimal() +
  scale_color_brewer(palette = "Dark2") +
  labs(
    x = "Total Key Events",
    y = "Average ROAS",
    color = "Channel Group"
  )
```
:::

------------------------------------------------------------------------

:::: {card}
::: {columns}
```{r fig.width=6, fig.height=4}
#| title: Cost Per Click
processed %>%
  ggplot(aes(x = reorder(channel_group, avg_cpc), y = avg_cpc, fill = channel_group)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  theme_classic() +
  scale_fill_brewer(palette = "Paired") +
  labs(x = "Channel Group", y = "Avg CPC")
```
:::

```{r fig.width=6, fig.height=4}
#| title: Return of Ad Spend
processed %>%
  ggplot(aes(x = avg_roas)) +
  geom_histogram(binwidth = 0.1, fill = "#007bff", color = "white") +
  theme_minimal() +
  labs(x = "Average ROAS", y = "Channel Count")
```
::::

------------------------------------------------------------------------

::: {.tabset card="📑 Top Channels"}
## Column - Plots

### By Total Events

```{r fig.width=8, fig.height=4}
#| title: By Total Events
processed %>%
  slice_max(total_events, n = 5) %>%
  ggplot(aes(x = reorder(channel_group, total_events), y = total_events, fill = channel_group)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  theme_minimal() +
  labs(x = "Channel Group", y = "Total Events")
```

### By Average ROAS

```{r fig.width=8, fig.height=4}
#| title: By Average ROAS
processed %>%
  slice_max(avg_roas, n = 5) %>%
  ggplot(aes(x = reorder(channel_group, avg_roas), y = avg_roas, fill = channel_group)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  theme_minimal() +
  labs(x = "Channel Group", y = "Average ROAS")
```
:::

------------------------------------------------------------------------

::: {card="📌 Key Insights"}
-   **Organic Search** and **Direct** channels drive the highest volume of key events.
-   **Paid channels** yield higher ROAS but lower event counts.
-   Combining CPC and ROAS metrics helps optimize budget allocation.
:::

------------------------------------------------------------------------
